Results

### 2021-07-08 Analysis/03_Summarise_results.Rmd
results up
Update 03_Summarise_results.Rmd

This script is the repeatable script for measuring changes in the different diversity metrics and how they are affected by the different stressors. 
In this section we are going to analyse the results from the `optim.replicates` chain.

# TODO
 - [ ] summarise.results: get ready to publish results tables
 - [ ] plot.results: get ready to publish plots (including results per methods and time per method)

>>>>

This script is the repeatable script for measuring changes in the different diversity metrics and how they are affected by the different stressors. 
In this section we are going to analyse the results from the `optim.replicates` chain

```{r}
## Loading the results
load("../Data/Processed/sim_equalizing.rda")
equalizing <- bkp
load("../Data/Processed/sim_facilitation.rda")
facilitation <- bkp
load("../Data/Processed/sim_filtering.rda")
filtering <- bkp
load("../Data/Processed/sim_competition.rda")
competition <- bkp
```

```{r}
## Loading the functions
source("../Functions/summarise.results.R")
source("../Functions/plot.results.R")
```

# Results per metrics

Here I'm going to display the results in box plot for each metric in each broad category.
> We can probably think of a better way to display the results in the future.

For each metric displayed here:

 * The different colours correspond to the different stressors (equalizing, facilitation, filtering and competition)
 * The different density of each colours correspond to the different levels of each stressor (removing 20, 40, 60 or 80% of the data)
 * All the metrics values are centred on the null (random) stressor for each individual simulation (i.e. 1 dataset is simulated, X% of the data is removed, one time randomly, one time biased - following the stressor; the metric is calculated on both the random and the biased removal and the biased removal is then centred on the random one (`biased metric score - random metric score`) for each simulation).
 * All the centred metric values are then scaled to the absolute maximum change (`centred scores/max(abs(centred scores))`).

```{r}
## Creating the list of results
all_results <- list(equalizing   = equalizing,
                    facilitation = facilitation,
                    filtering    = filtering,
                    competition  = competition)
## The different removal level names
removals <- c("20%", "40%", "60%", "80%")
## The colours
cols <- c("blue", "orange", "red", "green")
```

## Tree metrics

### Alpha

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "alpha", level.names = removals, col = cols)
```

### Dispersion

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "dispersion", level.names = removals, col = cols)
```

### Evenness

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "evenness", level.names = removals, col = cols, legend.pos = "bottomright")
```

## Dissimilarity metrics

### Rao

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_Rao", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Divergence (FD)

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_divergence", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Evenness (FD)

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "FD_evenness", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Melodic Rao

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "melodic_Rao", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Melodic MPD

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "melodic_mpd", level.names = removals, col = cols)
```

## Convex hull metrics

### Convex hull alpha

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "convex.hull", level.names = removals, col = cols)
```

## Hypervolume metrics

"hypervolume_richness"    
"hypervolume_dispersion"  
"hypervolume_regularity"

## Probability density metrics

"TPD_Richness"            
"TPD_Evenness"            
"TPD_Divergence"
